---
title: "Adoption of Climate-Resilient Groundnut Varieties Increases Agricultural Production, Consumption, and Smallholder Commercialization in West Africa"
subtitle: "Code to reproduce figures"
author: 'Martin Paul Jr. Tabe-Ojong, Jourdain Lokossou, Bisrat Gebrekidan, Hippolyte D. Affognon'
date: "Last updated: `r Sys.time()`"
output: 

 bookdown::pdf_document2:
    keep_tex: true
    template: HelperUtilities/my_templet.tex
 odt_document:
header-includes:
   - \usepackage[margin=2.8cm]{geometry}
   - \renewcommand{\contentsname}{Table of Contents}
   - \usepackage{enumitem}
   - \usepackage{pifont}
   - \renewcommand{\labelitemi}{$\rightarrow$}
   - \usepackage{tocloft}
   - \renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
   - \usepackage{hyperref}
   - \hypersetup{linkcolor = blue}
   - \usepackage{hanging}
   - \usepackage[T1]{fontenc}
   - \usepackage{graphicx}
   - \usepackage{booktabs,threeparttablex}
   - \usepackage{pdflscape}
   - \usepackage{fvextra}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
   - \usepackage{lmodern}
   - \usepackage{nimbusmono}
   - \renewcommand{\thetable}{SM\arabic{table}}
   - \setlength{\cfttabnumwidth}{1cm}

toc: false
toccolor: 'blue'
mainfont: 'lm'
toc-title: "-"
---
\newpage
\listoftables
\newpage


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = FALSE,
  warning = FALSE,
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 10),
  # if knitting to html disable the following line
  dev = "cairo_pdf",
  out.width = "100%"
)

options(width = 100)
# load the required libraries
extrafont::loadfonts()

# load the required libraries
pacman::p_load(
  sjlabelled,
  labelled,
  ggthemes,
  haven,
  openxlsx,
  tidyverse
)

#ggthemr(palette = 'light')
#my_font <- font_an
```


```{r}
source("HelperUtilities/Utils.R", local = knitr::knit_global())
my_font <- "Frutiger"
```

```{r}
data_for_plotting_ori <- read_csv("stata_outputs/figures_table/coefficent_plot_table.csv")%>%
  janitor::clean_names()

Groundnut_new <- read_dta("data/Groundnut.dta")
```

```{r}
df_plot <- data_for_plotting_ori%>%
  mutate(p.label = case_when(
    !is.na(aster) ~paste0(round(coef,3), aster) ,
    TRUE ~ paste0(round(coef,3), "")
  ) )
```

# Write a generic function

The `plot_coefficents` function allows to generate a coefficient plot with customizable aesthetics and filtering options, providing a visual representation of coefficient estimates, confidence intervals, and significance levels for different variables using the ggplot2 package in R. 

1. The function takes two arguments: `tbl_Num` and `X`, which determine the filtering and aesthetics of the plot, respectively.

2. The function filters the data frame `df_plot` based on the value of `tbl_Num`, keeping only the rows where the `tbl_no` variable matches `tbl_Num`.

3. The ggplot object `plt_tbl_1` is created, specifying the data frame `df_tbl_1` as the data and defining the aesthetics using `aes_string`. The `x` axis is set to the variable passed to the `X` argument, and the `y` axis is set to "coef". The color of the points is determined by the "inters_var" variable.

4. Several ggplot layers are added to the plot:
   - `geom_hline`: Adds a horizontal line at y = 0, representing the baseline/reference line.
   - `geom_point`: Adds points to the plot, representing coefficient estimates. The `position_dodge` function is used to separate the points based on the "inters_var" variable.
   - `geom_errorbar`: Adds error bars to the points, representing confidence intervals for the coefficient estimates.
   - `geom_text`: Adds text labels to the plot,  containing coefficient estimate and significance level . The labels are positioned using `position_dodge` to align them with the points.

5. Axis labels, facetting, and theme customization are applied:
   - `scale_x_discrete`: Sets custom labels for the x-axis categories.
   - `facet_wrap`: Creates separate plots for different levels of the `dep_var` variable.
   - `labs`: Sets the labels for the y-axis, title, subtitle, and x-axis.
   - `ggthemes::theme_base`: Applies a basic theme to the plot.
   - `theme`: Customizes various aspects of the plot, such as the legend position, text size and font, and panel appearance.

6. Finally, it returns the created plot object `plt_tbl_1`.



```{r}
plot_coefficents <- function(tbl_Num=2, X="inters_var"){
  
  df_tbl_1 <- df_plot%>%
  filter(tbl_no==tbl_Num)

  plt_tbl_1 <- 
    ggplot(df_tbl_1, aes_string(x = X, y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
  scale_x_discrete(labels=c("Adoption", "Area under\nadoption (ha)")) +
    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
       strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  
  return(plt_tbl_1)
  
}
```

# Figure 1. Kernel density distribution outcome variables

```{r}

# gprod
df_gprod <- Groundnut_new%>%
  select(id, gprod,adopt)%>%
  filter(gprod < 5000)
df_gprod$adopt <- factor(df_gprod$adopt, levels = c(0,1), labels = c("Non-adopters","Adopters"))

mean_data <- aggregate(gprod ~ adopt, data = df_gprod, FUN = mean)




fig_gprod <- ggplot(df_gprod, aes(x = gprod, fill = factor(adopt), color = factor(adopt)), show.legend = T) +
  geom_density(alpha = 0.06,kernel="epanechnikov", bw=200, show.legend = T) +
  geom_vline(data = mean_data, aes(xintercept = gprod), size = 1, alpha=0.2, show.legend = F) +
geom_text(data = mean_data, aes(x = gprod, label = paste("μ", ifelse(adopt == "Adopters", "adopters", "non-adopters"), "=", round(gprod, 2)), y = 0.0009), vjust = -0.5, angle = 90,family=my_font, show.legend = F, size=4) +
  ylim(c(0, 0.00118))+
  labs(x = "Production(Kg)", y = "Density", fill = "Adopt") +
  #scale_fill_manual(values = c("blue", "red")) +
  scale_color_brewer(palette="Set1")+ 
  guides(fill = "none")+
  #scale_fill_brewer(palette="Set1")+
  #scale_color_manual(values = c("non-adopters" = "blue", "adopters" = "red")) +
  theme_base(base_family = my_font)+
  theme(panel.grid.major.y = element_blank(),
          legend.position = c(0.80,0.8),
          legend.title = element_blank())

fig_gprod
# qsale
df_qsale <- Groundnut_new%>%
  select(id, adopt,qsale)%>%
  filter(qsale < 4000)
df_qsale$adopt <- factor(df_qsale$adopt, levels = c(0,1), labels = c("Non-adopters","Adopters"))

mean_data <- aggregate(qsale ~ adopt, data = df_qsale, FUN = mean)


df_export <- Groundnut_new%>%
  select(adopt,qsale,gprod)%>%
  filter(qsale < 4000 & gprod < 5000)%>%
  mutate(adopt=factor(adopt, levels = c(0,1), labels = c("Non-adopter","Adopter")))

write_csv(df_export, "stata_outputs/figures_table/Figure1.csv")

fig_qsale <- ggplot(df_qsale, aes(x = qsale, fill = factor(adopt), color = factor(adopt)), show.legend = T) +
  geom_density(alpha = 0.06,kernel="epanechnikov", bw=200, show.legend = F) +
  geom_vline(data = mean_data, aes(xintercept = qsale), size = 1, alpha=0.2, show.legend = F) +
geom_text(data = mean_data, aes(x = qsale, label = paste("μ", ifelse(adopt == "Adopters", "adopters", "non-adopters"), "=", round(qsale, 2)), y = 0.0009), vjust = -0.5, angle = 90,family=my_font, show.legend = F, size=4) +
  ylim(c(0, 0.00118))+
  labs(x = "Commercialization(Kg)", y = "", fill = "Adopt") +
  #scale_fill_manual(values = c("blue", "red")) +
  scale_color_brewer(palette="Set1")+ 
  guides(fill = "none")+
  #scale_fill_brewer(palette="Set1")+
  #scale_color_manual(values = c("non-adopters" = "blue", "adopters" = "red")) +
  theme_base(base_family = my_font)+
  theme(panel.grid.major.y = element_blank(),
        text = element_text(size = 14),
          legend.position = "bottom",
          legend.title = element_blank())
fig_qsale

fig_1 <- fig_gprod + fig_qsale+ 
  patchwork::plot_annotation(tag_levels = 'I')
fig_1
ggsave("figures/fig_1.pdf", plot = fig_1, width = 35, height = 15, units = "cm",device = cairo_pdf)
```



# Figure 2. Adoption rate over time

```{r}
adoption_data <- Groundnut_new%>%
  select(year, country, adopt)

df <- adoption_data%>%
  group_by(year, country, adopt)%>%
  summarise(count = n()) %>%
   mutate(ptg = round(prop.table(count) *
        100, 1))%>%
  filter(adopt==1)%>%
  mutate(year= factor(year))%>%
  mutate(my_lable =case_when(
    (ptg==17 || ptg == 55) ~  paste0(ptg, ".0"),
    TRUE ~  paste0(ptg)
  ))

ss <- ggplot(df, aes(x = country,
    y = ptg)) + geom_bar(aes(fill = year),
    stat = "identity",
    color = "white",
    position = position_dodge(0.8),
    size = 0.3, alpha = 0.9,
    width = 0.7) + 
  geom_text(aes(
    label = my_lable,group=year), color = "black",  vjust=-0.3, family=my_font,size=5,
    position = position_dodge(.8)) +
    theme_bw(base_family = my_font,
    base_size = 16) +
  labs(y="Percent of households", x=NULL)+
    scale_y_continuous(labels = scales::label_percent(scale = 1)) +
    scale_fill_manual(values = c("#30469c","#8c0049", "#EEAB73")) +
    #scale_fill_manual(values = c("#305596", "#305596", "#305596"))+
  ylim(c(0,60)) +
    theme(panel.grid.major.y = element_blank(),
          legend.position = "bottom",
          legend.title = element_blank(),
          axis.title = element_text(color = "#51585F"),
        panel.grid.major.x = element_line(size = 0.3),
        panel.grid.minor.y = element_line(size = 0.3), panel.border = element_rect(colour = "grey60"))

ss

ggsave("figures/fig_2.pdf", plot = ss, width = 20, height = 15, units = "cm",device = cairo_pdf)
```
# Figure 3. 2SLS estimates of the relationship between adoption, production, and yields

```{r}
 df_tbl_3 <- df_plot%>%
  filter(tbl_no==3)%>%
  mutate(dep_var=factor(dep_var, levels = c("Yield","Production value", "Consumption"),labels  = c("[A] Yield","[B] Production value", "[C] Consumption")))

  
plt_tbl_3 <- 
    ggplot(df_tbl_3, aes_string(x = "inters_var", y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
  scale_x_discrete(labels=c("Adoption\n(Yes/No) ", "Area under\nadoption (ha)")) +
  scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73"))+
    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),

      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_3
  
  ggsave("figures/fig_3.pdf", plt_tbl_3, width = 32, height = 18, units = "cm",device = cairo_pdf)
```

# Figure 4. 2SLS estimates of the relationship between adoption and commercialization.

```{r}
df_tbl_4 <- df_plot%>%
  filter(tbl_no==4)%>%
  mutate(inters_var = factor(inters_var, labels = c(`Adoption dummy` = "Adoption\n(Yes/No)" , 
        `Area under adoption (ha)`="Area under\n adoption (ha)")))%>%
  mutate(dep_var=factor(dep_var, levels = c("Market participation","Quantity Sold", "Sale Value"),labels  = c("[A] Market participation","[B] Quantity sold", "[C] Sales value")))
plt_tbl_4 <- 
    ggplot(df_tbl_4, aes_string(x = "model_type", y = "coef", color="model_type")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 3.5,
      family = my_font
    ) +
    scale_x_discrete(labels=c("Correlated\nrandom effects ", "Fixed\nEffects")) +
    facet_grid(inters_var~dep_var, scales = "free") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
     scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73"))+

    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black"
      ),strip.text.y = element_text(family = my_font, size = 12))

plt_tbl_4

ggsave("figures/fig_4.pdf", plt_tbl_4, width = 24, height = 16, units = "cm",device = cairo_pdf)

```
# Figure 5. 2SLS estimates of the relationship between continuous adoption and commercialization.

```{r}
df_tbl_5 <- df_plot%>%
  filter(tbl_no==5)%>%
  mutate(dep_var=factor(dep_var, levels = c("Yield", "Consumption","Quantity Sold"),labels  = c("[A] Yield", "[B] Consumption","[C] Quantity sold")))


plt_tbl_5 <- 
    ggplot(df_tbl_5, aes_string(x = "inters_var", y = "coef", color="inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_x_discrete(labels=c("Sustained adoption\n(3 years)")) +
       scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73"))+

    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
     legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
       strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black"
      ))


plt_tbl_5
ggsave("figures/fig_5.pdf", plt_tbl_5, width = 26, height = 12, units = "cm",device = cairo_pdf)

```
# Figure 6. Cross-country analysis of adoption and commercialization

```{r}


df_tbl_6 <- df_plot%>%
  filter(tbl_no==6)%>%
  mutate(dep_var=factor(dep_var, levels = c("Yield", "Consumption", "Quantity Sold"),labels = c("[A] Yield", "[B] Consumption", "[C] Quantity sold")))

  plt_tbl_6 <- 
    ggplot(df_tbl_6, aes_string(x = "country", y = "coef", color="country")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.8),
      #vjust = 0.5 * -1.5,
      
      hjust = 1.2,
      show.legend = FALSE,
      size = 3.5,
      family = my_font
    ) +
    #scale_x_discrete(labels=c("Commercialization", "Yield")) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73"))+

    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
       strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  
  
  plt_tbl_6
  ggsave("figures/fig_6_new.svg", plt_tbl_6, width = 35, height = 18, units = "cm", dpi = 300)
  ggsave("figures/fig_6.pdf", plt_tbl_6, width = 40, height = 16, units = "cm", dpi = 300,device = cairo_pdf)
```

# Figure 7 2SLS estimates of the relationship between adoption and commercialization.

```{r}
df_tbl_10 <- df_plot%>%
  filter(tbl_no==7)%>%
  mutate(inters_var=factor(inters_var, levels=c("Quantity harvested", "Quantity Consumed"), labels=c("Quantity\nHarvested", "Quantity\nConsumed")))%>%
  mutate(coef2 = formatC(coef, format = "e", digits=2)    )%>%
  mutate(p_label2 = paste0(coef2,aster))%>%
  mutate(dep_var=factor(dep_var, levels = c("Market participation","Quantity Sold", "Sale Value"),labels  = c("[A] Market participation","[B] Quantity sold", "[C] Sales value")))
plt_tbl_10 <- 
    ggplot(df_tbl_10, aes_string(x = "inters_var", y = "coef")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p_label2"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 3,
      family = my_font
    ) +
    #scale_x_discrete(labels=c("Correlated\nrandom effects ", "Fixed\nEffects")) +
    facet_grid(.~dep_var, scales = "free") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
  scale_y_continuous(labels = scales::scientific_format())+
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
       strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black"
      ),strip.text.y = element_text(family = my_font, size = 12))

plt_tbl_10

ggsave("figures/fig_7.pdf", plt_tbl_10, width = 26, height = 18, units = "cm",device = cairo_pdf)

```

# Figure SM1. OLS estimates of the relationship between adoption and commercialization

```{r}
 df_tbl_sm1 <- df_plot%>%
  filter(tbl_no==1) %>% mutate(dep_var=factor(dep_var, levels = c("Market participation","Quantity Sold", "Sale Value"),labels  = c("[A] Market participation","[B] Quantity sold", "[C] Sales value")))


  plt_tbl_sm1 <- 
    ggplot(df_tbl_sm1, aes_string(x = "inters_var", y = "coef",color = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
  scale_x_discrete(labels=c("Adoption", "Area under\nadoption (ha)")) +
        scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73"))+

    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
       strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_sm1
  
  ggsave("figures/fig_SM1.pdf", plt_tbl_sm1, width = 30, height = 15, units = "cm",device = cairo_pdf)
```

# Figure SM2. OLS estimates of the relationship between adoption, production, and yields

```{r}
 df_tbl_sm2 <- df_plot%>%
  filter(tbl_no==2)%>%
  mutate(dep_var=factor(dep_var, levels = c("Yield","Production", "Production value"),labels  = c("[A] Yield","[B] Production", "[C] Production value")))

  plt_tbl_sm2 <- 
    ggplot(df_tbl_sm2, aes_string(x = "inters_var", y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.15,
      show.legend = FALSE,
      size = 4.5,
      family = my_font
    ) +
    scale_color_manual(values = c("#30469c","#8c0049", "#EEAB73"))+
    
  scale_x_discrete(labels=c("Adoption", "Area under\nadoption (ha)")) +
    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
       strip.background = element_rect(fill = adjustcolor("#0F75E0", alpha.f = 0.8), color = "#0F75E0"),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_sm2
  
  ggsave("figures/fig_SM2.pdf", plt_tbl_sm2, width = 35, height = 15, units = "cm",device = cairo_pdf)
```
```{r}
library(openxlsx)
# Split the data frame based on Category column

df_export <- data_for_plotting_ori%>%
  rename(`Interest variables` = inters_var, `Outcome variables` = dep_var, Coefficent = coef, `Robust standard error`=se, `P-Value` = pval, Significance = aster, `Confidence Interval (lower)`= ci_low,`Confidence Interval (upper)`=ci_high, `R-Square`= r_sqr, `Model type` = model_type, Country = country)

df_list <- split(df_export, df_export$tbl_no)

# Create a new workbook
wb <- createWorkbook()

# Save each subset as an Excel sheet
for (i in seq_along(df_list)) {
  sheet_name <- paste("Figure_", names(df_list)[i], sep = "")
  addWorksheet(wb, sheetName = sheet_name)
  writeData(wb, sheet = sheet_name, x = df_list[[i]])
}

# Save the workbook as an Excel file
saveWorkbook(wb, "Source_Data_2_0.xlsx", overwrite = TRUE)
```


