---
title: "Technology Adoption and Smallholder Commercialization: Panel Evidence from Groundnut Farmers in West Africa"
subtitle: "Supplementary Material (Descriptive statistics)"
date: "Last updated: `r Sys.time()`"
output: 

 bookdown::pdf_document2:
    keep_tex: true
    template: HelperUtilities/my_templet.tex
 odt_document:
header-includes:
   - \usepackage[margin=2.8cm]{geometry}
   - \renewcommand{\contentsname}{Table of Contents}
   - \usepackage{enumitem}
   - \usepackage{pifont}
   - \renewcommand{\labelitemi}{$\rightarrow$}
   - \usepackage{tocloft}
   - \renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
   - \usepackage{hyperref}
   - \hypersetup{linkcolor = blue}
   - \usepackage{hanging}
   - \usepackage[T1]{fontenc}
   - \usepackage{graphicx}
   - \usepackage{booktabs,threeparttablex}
   - \usepackage{pdflscape}
   - \usepackage{fvextra}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
   - \usepackage{lmodern}
   - \usepackage{nimbusmono}
   - \renewcommand{\thetable}{SM\arabic{table}}
   - \setlength{\cfttabnumwidth}{1cm}

toc: false
toccolor: 'blue'
mainfont: 'lm'
toc-title: "-"
---
\newpage
\listoftables
\newpage


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = FALSE,
  warning = FALSE,
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 10),
  # if knitting to html disable the following line
  dev = "cairo_pdf",
  out.width = "100%"
)

options(width = 100)
# load the required libraries
extrafont::loadfonts()

# load the required libraries
pacman::p_load(
  jsonlite,
  sjlabelled,
  labelled,
  dataMaid,
  plotly,
  wesanderson,
  ggthemes,
  hrbrthemes,
  sjmisc,
  expss,
  haven,
  ggstream,
  ggthemr,
  ggstatsplot,
  highcharter,
  gtsummary,
  tidyverse
)

ggthemr(palette = 'light')
#my_font <- font_an
```


```{r}

source("HelperUtilities/Utils.R", local = knitr::knit_global())
my_font <- "Frutiger"
```

```{r}
data_for_plotting_ori <- read_csv("data/for_plot/data_for_plotting.csv")%>%
  janitor::clean_names()

Groundnut_new <- read_dta("data/for_plot/data_for_descriptive.dta")
```

```{r}
df_plot <- data_for_plotting_ori%>%
  mutate(p.label = case_when(
    !is.na(aster) ~paste0(coef, aster) ,
    TRUE ~ paste0(coef, "")
  ) )
```

# Write a generic function

```{r}
plot_coefficents <- function(tbl_Num=2, X="inters_var"){
  
  df_tbl_1 <- df_plot%>%
  filter(tbl_no==tbl_Num)

  plt_tbl_1 <- 
    ggplot(df_tbl_1, aes_string(x = X, y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
  scale_x_discrete(labels=c("Adoption", "Area under\nadoption (ha)")) +
    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#95BAFF", alpha.f = 0.6)),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  
  return(plt_tbl_1)
  
}
```

# OLS estimates of the relationship between adoption and commercialization

```{r}

plt_2 <- plot_coefficents(tbl_Num = 2)
plt_2

ggsave("plots/plt2.png", plt_2, width = 22, height = 12, units = "cm")
```

```{r}
 df_tbl_1 <- df_plot%>%
  filter(tbl_no==2 | tbl_no==3)

  plt_tbl_1 <- 
    ggplot(df_tbl_1, aes_string(x = "inters_var", y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
  scale_x_discrete(labels=c("Adoption", "Area under\nadoption (ha)")) +
    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#95BAFF", alpha.f = 0.6)),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  plt_tbl_1
  
  ggsave("plots/plt2and3.png", plt_tbl_1, width = 30, height = 18, units = "cm")
```

# OLS estimates of the relationship between adoption, production and yields

```{r}
plt_3 <- plot_coefficents(tbl_Num = 3)
plt_3
ggsave("plots/plt3.png", plt_3, width = 27, height = 12, units = "cm")

```

# 2SLS estimates of the relationship between adoption and commercialization

```{r}
df_tbl_4 <- df_plot%>%
  filter(tbl_no==4 |tbl_no==5)%>%
  mutate(inters_var = factor(inters_var, labels = c(`Adoption dummy` = "Adoption\ndummy" , 
        `Area under adoption (ha)`="Area under\n adoption (ha)")))
plt_tbl_4 <- 
    ggplot(df_tbl_4, aes_string(x = "model_type", y = "coef", colour = "model_type")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 3.5,
      family = my_font
    ) +
    scale_x_discrete(labels=c("Correlated\nrandom effects ", "Fixed\nEffects")) +
    facet_grid(inters_var~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#95BAFF", alpha.f = 0.6)),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black"
      ),strip.text.y = element_text(family = my_font, size = 12))

plt_tbl_4

ggsave("plots/plt4_5.png", plt_tbl_4, width = 24, height = 16, units = "cm")

```

```{r}
df_tbl_4 <- df_plot%>%
  filter(tbl_no==4)

plt_tbl_4 <- 
    ggplot(df_tbl_4, aes_string(x = "model_type", y = "coef", colour = "model_type")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 3.5,
      family = my_font
    ) +
    scale_x_discrete(labels=c("Correlated\nrandom effects ", "Fixed\nEffects")) +
    facet_grid(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#95BAFF", alpha.f = 0.6)),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black"
      ),strip.text.y = element_text(family = my_font, size = 12))

plt_tbl_4

ggsave("plots/plt4.png", plt_tbl_4, width = 24, height = 16, units = "cm")

```
# 2SLS estimates of the relationship between adoption and commercialization (Area)

```{r}
df_tbl_5 <- df_plot%>%
  filter(tbl_no==5)

plt_tbl_5 <- 
    ggplot(df_tbl_5, aes_string(x = "model_type", y = "coef", colour = "model_type")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
    scale_x_discrete(labels=c("Correlated\nrandom effects ", "Fixed\nEffects")) +
    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
     legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#95BAFF", alpha.f = 0.6)),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black"
      ))

plt_tbl_5
ggsave("plots/plt5.png", plt_tbl_5, width = 26, height = 12, units = "cm")

```
# 2SLS estimates of the relationship between area under adoption and commercialization

```{r}

plt_6 <- plot_coefficents(tbl_Num = 6)
plt_6
ggsave("plots/plt6.png", plt_6, width = 30, height = 12, units = "cm")


```
```{r}
plt_7 <- plot_coefficents(tbl_Num = 7)+
  scale_x_discrete(labels = c("Sustained adoption\n(3years)"))

plt_7

ggsave("plots/plt7.png", plt_7, width = 24, height = 12, units = "cm")


```

```{r}
df_tbl_7_2 <- df_plot%>%
  filter(tbl_no==7)

  plt_tbl_7_2 <- 
    ggplot(df_tbl_7_2, aes_string(x = "dep_var", y = "coef", colour = "dep_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.6),
      #vjust = 0.5 * -1.5,
      hjust = -0.2,
      show.legend = FALSE,
      size = 4,
      family = my_font
    ) +
  # scale_x_discrete(labels=c("Adoption", "Area under\nadoption (ha)")) +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("black", alpha.f = 0.6)),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "white"
      ))
  
  plt_tbl_7_2
  
  ggsave("plots/plt7_2.png", plt_tbl_7_2, width = 20, height = 12, units = "cm")

```

```{r}


df_tbl_9 <- df_plot%>%
  filter(tbl_no==9)

  plt_tbl_9 <- 
    ggplot(df_tbl_9, aes_string(x = "country", y = "coef", colour = "country")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.55),
      #vjust = 0.5 * -1.5,
      hjust = -0.18,
      show.legend = FALSE,
      size = 3,
      family = my_font
    ) +
    #scale_x_discrete(labels=c("Commercialization", "Yield")) +
    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#95BAFF", alpha.f = 0.6)),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  
  plt_tbl_9
   ggsave("plots/plt9.png", plt_tbl_9, width = 25, height = 13, units = "cm")
```
```{r}


df_tbl_8 <- df_plot%>%
  filter(tbl_no==8)

  plt_tbl_8 <- 
    ggplot(df_tbl_8, aes_string(x = "inters_var", y = "coef", colour = "inters_var")) +
    geom_hline(
      yintercept = 0,
      size = 0.3,
      color = "grey"
    ) +
    geom_point(position = position_dodge(0.3), size = 3) +
    geom_errorbar(
      aes_string(ymin = "ci_low", ymax = "ci_high"), 
      position = position_dodge(0.4),
      width = 0.1
    ) +
    geom_text(
      aes_string(label = "p.label"),
      position = position_dodge(0.55),
      #vjust = 0.5 * -1.5,
      hjust = -0.18,
      show.legend = FALSE,
      size = 3.2,
      family = my_font
    ) +
    scale_x_discrete(labels=c("Direct\nEffect", "Indirect\nEffect", "Total\nEffect")) +
    facet_wrap(~dep_var, scales = "free_y") +
    labs(
      y = "Estimates(95% Robust CI)",
      title = "",
      subtitle = "",
      x = ""
    ) +
    ggthemes::theme_base() +
    theme(
      legend.position = "none",
      text = element_text(family = my_font, size = 14),
      axis.text = element_text(family = my_font, size = 14),
      strip.background = element_rect(fill = adjustcolor("#95BAFF", alpha.f = 0.6)),
      panel.border = element_rect(size = 0, fill = NA),
      strip.text = element_text(
        family = my_font,
        size = 14, color = "black" ))
  
  plt_tbl_8
   ggsave("plots/plt8.png", plt_tbl_8, width = 22, height = 12, units = "cm")
```