---
title: "Technology Adoption and Smallholder Commercialization: Panel Evidence from West Africa"
subtitle: "Supplementary Information (Full model tables and robustness check)"
date: "Last updated: `r Sys.time()`"
output: 
 bookdown::pdf_document2:
    keep_tex: true
    template: HelperUtilities/my_templet.tex
    #highlight: zenburn
header-includes:
   - \usepackage[margin=2.8cm]{geometry}
   - \renewcommand{\contentsname}{Table of Contents}
   - \usepackage{enumitem}
   - \usepackage{pifont}
   - \renewcommand{\labelitemi}{$\rightarrow$}
   - \usepackage{tocloft}
   - \renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
   - \usepackage{hyperref}
   - \hypersetup{linkcolor = blue}
   - \usepackage{hanging}
   - \usepackage[T1]{fontenc}
   - \usepackage{graphicx}
   - \usepackage{booktabs,threeparttablex}
   - \usepackage{pdflscape}
   - \usepackage{fvextra}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
   - \usepackage{lmodern}
   - \usepackage{nimbusmono}
   - \renewcommand{\thetable}{SM\arabic{table}}
   - \setlength{\cfttabnumwidth}{1cm}

toc: false
toccolor: 'blue'
mainfont: 'lm'
toc-title: "Table of Contents"
---

```{r setup, include=FALSE, warning=FALSE, comment=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 60),
  out.width = "100%"
)

options(width = 100)
# load the required libraries



# load the required libraries
pacman::p_load(
jsonlite,
sjlabelled,
labelled,
dataMaid,
plotly,
wesanderson,
ggthemes,
hrbrthemes,
sjmisc,
expss,
haven,
knitr,
kableExtra,
ggstream,
ggstatsplot,
gtsummary,
highcharter,
tidyverse
)
```
\newpage
\tableofcontents
\newpage
\listoftables
\newpage

```{r, echo=FALSE}
list_of_tables <- list()
file_names <- list.files(here::here("data", "for_latex"), pattern = "*.txt")

for(i in 1:length(file_names)){
  list_of_tables[[i]] <- readr::read_delim(here::here("data","for_latex", file_names[[i]]), delim = "\t", escape_double = FALSE, trim_ws = TRUE, skip = 1,na = "empty" )
}


names(list_of_tables) <- str_replace(file_names, ".txt", "")


change_names <- function(df){
  names(df) <- str_replace(names(df), "_", "-")
  return(df)
}

list_of_tables <- purrr::map(list_of_tables, change_names)

clean_space <- function(df) {
  df %>%
    mutate_all(~ (str_replace_all(., "%", "\\\\%")))
}

list_of_tables <- purrr::map(list_of_tables, clean_space)


color_significance <- function(df){
  df[-1] <- lapply(
  df[-1], function(x){
    cell_spec(x, background = ifelse(str_count(x, "\\*")==1, "#8C298133", ifelse(str_count(x, "\\*")==2, "#641A8033", ifelse(str_count(x, "\\*")==3, "#3C0F7033", "white"))),color = ifelse(str_count(x, "\\*")>=1, "White", "black" ),bold = ifelse(str_count(x, "\\*")>=1,T, F ))
  }
)
  
  return(df)
}

Groundnut_new <- read_dta("data/for_plot/data_for_descriptive.dta")%>%
  sjlabelled::var_labels(
    year = "Waves of the study",
    country = "Country",
    sales_value = "Sales value",
    prod_value = "Production value",
    gprod = "Total quantity of groundnut harvested",
    formarrach = "Training on groundnut farming",
    cooperative = "Farmers group membership"
  )%>%
  mutate(
    formarrach = haven::as_factor(formarrach),
    cooperative = haven::as_factor(cooperative)
    
  )
my_vars <- c(
  "country",
  "year",
  "adopt",
  "improvsup",
  "sellers",
  "qsale",
  "sales_value",
  "gprod",
  "prod_value",
  "gyield",
  "age",
  "sexe",
  "nbschool",
  "hhsize",
  "cooperative",
  "formagri",
  "formarrach",
  "visitpublic",
  "extension",
  "credite",
  "creditn",
  "dmurbain",
  "dmvillage",
  "crotation",
  "cmixt",
  "nbrhoejour",
  "uprice",
  "cseed_ha",
  "cfert_ha",
  "cpest_ha",
  "clabor_ha",
  "gsize",
  "off_farm",
  "dratio",
  "typsoil1",
  "typsoil2",
  "typsoil3",
  "adopt2y",
  "adopt3y"
)

my_vars_2 <- c(
  "country",
  "year",
  "adopt",
  "age",
  "sexe",
  "nbschool",
  "hhsize",
  "dratio",
  "cooperative_2",
  "formagri",
  "formarrach_2",
  "visitpublic",
  "extension",
  "credite",
  "creditn",
  "dmurbain",
  "dmvillage",
  "crotation",
  "cmixt",
  "nbrhoejour",
  "uprice",
  "cseed_ha",
  "cfert_ha",
  "cpest_ha",
  "clabor_ha",
  "gsize",
  "off_farm",
  "typsoil1",
  "typsoil2",
  "typsoil3"
)

```
\newpage
# Descriptive statistics

```{r}
Groundnut_new_2 <- Groundnut_new%>%
  mutate(cooperative_2 = case_when(
    str_detect(cooperative, "Yes") ~ 1,
    TRUE ~ 0
  ),
  formarrach_2 = case_when(
    formarrach=="No" ~ 0,
    TRUE ~ 1
  ))%>%
  sjlabelled::var_labels(
    cooperative_2= "Farmers group membership (dummy)",
    formarrach_2 = "Training on groundnut farming(dummy)"
  )

tbl_strata_ex1 <-
  Groundnut_new_2 %>%
  select(my_vars_2, -c(cooperative,formarrach))%>%
  mutate(adopt = factor(adopt, labels=c("Non-adopter", "Adopter")))%>%
  tbl_strata(
    strata = year,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(
    by=adopt,
    type = list(c(sexe,credite,creditn,formagri) ~ "dichotomous", c(extension)~"continuous"),
    missing = "no",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  )%>% add_p(),
    .header = "**{strata}**, N = {n}"
  )

disc_tbl <- tbl_strata_ex1%>%
  # convert to kableExtra
  as_kable_extra(booktabs = TRUE, longtable = F,caption="Descriptive statistics by year and adoption status") %>%
  # reduce font size to make table fit. 
  # you may also use the `latex_options =  c( c("scale_down", "hold_position"), "hold_position")` argument here.
  kableExtra::kable_styling(font_size = 6, latex_options =  c("scale_down", "hold_position", "repeat_header"))%>%
  kableExtra::landscape()%>%
  row_spec(33, hline_after  = T)
disc_tbl

```
\newpage

# Pooled OLS Regressions

```{r}

df <- list_of_tables$SM1_Table3%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)




kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full OLS estimates of the relationship between adoption and commercialization(Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  kableExtra::kable_paper()
```
\newpage

```{r}

df <- list_of_tables$SM1_Table3_Area%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)



kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full OLS estimates of the relationship between adoption and commercialization (Area under Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

\newpage

```{r}

df <- list_of_tables$SM2_Table4%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = " Full OLS estimates of the relationship between adoption, production and yields(Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

\newpage

```{r}

df <- list_of_tables$SM2_Table4_Area%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr",  caption = "OLS estimates of the relationship between adoption, production and yields(Area under Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
kable_classic("striped", full_width = F)
```
\newpage
# Panel Regression

```{r}

df <- list_of_tables$SM3_Table5%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)%>%
  filter(!stringr::str_detect(variables, 'district') )



kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between adoption and commercialization(Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```
\newpage

```{r}

df <- list_of_tables$SM4_Table6%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between adoption and commercialization (Area under Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

\newpage

```{r}

df <- list_of_tables$SM5_Table7%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)



kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between adoption, production and yields")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
landscape()
```
\newpage

```{r}

df <- list_of_tables$SM6_adopt_3y%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)%>%
  mutate(
   variables = gsub("\\(.*", "", variables)
  )



kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between continous adoption, production and yields")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
landscape()
```


\newpage
# Correlated random effects

```{r}
df <- list_of_tables$cre_tbl_adopt%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full Correlated random effects estimations of the relationship between adoption , commercialization and market orientation")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()
```

```{r}
df <- list_of_tables$cre_tbl_area%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full Correlated random effects estimations of the relationship between adoption (area), commercialization and market orientation")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()
```
\newpage

# Causal mediation analysis

```{r}
df <- list_of_tables$mediation_prod%>%
  rename(variables = VARIABLES)%>%
  mutate(variables = case_when(
    variables == "total" ~ "Total effect (TE)",
    variables == "effect" ~ "Direct effect",
    variables == "direct" ~ "Indirect effect",
    TRUE ~ variables
  ))

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Linear IV mediation analysis of adoption and commercialization (production)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

```{r}
df <- list_of_tables$mediation_yield%>%
  rename(variables = VARIABLES)%>%
  mutate(variables = case_when(
    variables == "total" ~ "Total effect (TE)",
    variables == "effect" ~ "Direct effect",
    variables == "direct" ~ "Indirect effect",
    TRUE ~ variables
  ))

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Linear IV mediation analysis of adoption and commercialization (Yield)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```


```{r}
df <- list_of_tables$PMed_adopt_3y%>%
  rename(variables = VARIABLES)%>%
  mutate(variables = case_when(
    variables == "total" ~ "Total effect (TE)",
    variables == "effect" ~ "Direct effect",
    variables == "direct" ~ "Indirect effect",
    TRUE ~ variables
  ))

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Linear IV mediation analysis of continuous adoption and commercialization (Production)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```


```{r}
df <- list_of_tables$YMed_adopt_3y%>%
  rename(variables = VARIABLES)%>%
  mutate(variables = case_when(
    variables == "total" ~ "Total effect (TE)",
    variables == "effect" ~ "Direct effect",
    variables == "direct" ~ "Indirect effect",
    TRUE ~ variables
  ))

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Linear IV mediation analysis of continuous adoption and commercialization (Yield)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()
```

# Robustness checks
\newpage

## Cross country analysis

```{r}
df <- list_of_tables$cross_country_t%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F,col.names = c("variables", "Yield", "Commercialization", "Yield", "Commercialization", "Yield", "Commercialization"), align="lrrr", caption = "2SLS estimates of the relationship between  adoption and commercialization and yield across countries")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()%>%
add_header_above(c(" ", "Ghana" = 2, "Mali" = 2, "Nigeria" = 2)) 
```


\newpage
## Control function approach

```{r}

df <- list_of_tables$SM7_CF_Ro%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full Control function estimations of the relationship between adoption and market participation")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()
```
\newpage
## Using acesss as lone IV
```{r}

df <- list_of_tables$SM8_Access_Ro%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)



kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between adoption, commercialization, production and yield (instrument for access)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()
```
\newpage
## Hausman Taylor IV

```{r}

df <- list_of_tables$SM9_HTIV_Ro%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full HAUSMAN TAYLOR IV estimations")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```
\newpage
## Lewbels Test

```{r}

df <- list_of_tables$SM10_LT%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)%>%
  mutate(
    #variables = str_remove_all(variables, "(centered)"),
    #variables = str_remove_all(variables, "()"),
    #variables = str_remove_all(variables, "cen"),
    variables = gsub("\\(.*", "", variables)
  )%>%
  filter(MP != "-")

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full Lewbel instrumental variable estimations of the relationship between adoption and commercialization")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```
\newpage

## Continuous adoption (2 years)

```{r}
df <- list_of_tables$IVReg_adopt_2y%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)%>%
  mutate(
    #variables = str_remove_all(variables, "(centered)"),
    #variables = str_remove_all(variables, "()"),
    #variables = str_remove_all(variables, "cen"),
    variables = gsub("\\(.*", "", variables)
  )

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between continuous adoption (two-year) and commercialization")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

```{r}
df <- list_of_tables$PMed_adopt_2y%>%
  rename(variables = VARIABLES)%>%
  mutate(variables = case_when(
    variables == "total" ~ "Total effect (TE)",
    variables == "effect" ~ "Direct effect",
    variables == "direct" ~ "Indirect effect",
    TRUE ~ variables
  ))

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Linear IV mediation analysis of continuous adoption (2 Years) and commercialization (Production)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

```{r}
df <- list_of_tables$YMed_adopt_2y%>%
  rename(variables = VARIABLES)%>%
  mutate(variables = case_when(
    variables == "total" ~ "Total effect (TE)",
    variables == "effect" ~ "Direct effect",
    variables == "direct" ~ "Indirect effect",
    TRUE ~ variables
  ))

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Linear IV mediation analysis of continuous adoption (2 Years) and commercialization (Yield)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

