---
title: "The Adoption of Climate-Resilient Groundnut Varieties Increases Agricultural Production and Smallholder Commercialization in West Africa"
subtitle: "Supplementary Information (Full model tables and robustness check)"
date: "Last updated: `r Sys.time()`"
output: 
 bookdown::pdf_document2:
    keep_tex: true
    template: HelperUtilities/my_templet.tex
    #highlight: zenburn
header-includes:
   - \usepackage[margin=2.8cm]{geometry}
   - \renewcommand{\contentsname}{Table of Contents}
   - \usepackage{enumitem}
   - \usepackage{pifont}
   - \renewcommand{\labelitemi}{$\rightarrow$}
   - \usepackage{tocloft}
   - \renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
   - \usepackage{hyperref}
   - \hypersetup{linkcolor = blue}
   - \usepackage{hanging}
   - \usepackage[T1]{fontenc}
   - \usepackage{graphicx}
   - \usepackage{booktabs,threeparttablex}
   - \usepackage{pdflscape}
   - \usepackage{fvextra}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
   - \usepackage{lmodern}
   - \usepackage{nimbusmono}
   - \renewcommand{\thetable}{SM\arabic{table}}
   - \setlength{\cfttabnumwidth}{1cm}

toc: false
toccolor: 'blue'
mainfont: 'lm'
toc-title: "Table of Contents"
---

```{r setup, include=FALSE, warning=FALSE, comment=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 60),
  out.width = "100%"
)

options(width = 100)
# load the required libraries



# load the required libraries
pacman::p_load(
jsonlite,
sjlabelled,
labelled,
dataMaid,
plotly,
wesanderson,
ggthemes,
hrbrthemes,
sjmisc,
expss,
haven,
knitr,
kableExtra,
ggstream,
ggstatsplot,
gtsummary,
highcharter,
tidyverse
)
```
\newpage
\tableofcontents
\newpage
\listoftables
\newpage









\newpage
```{r, echo=FALSE}
list_of_tables <- list()
file_names <- list.files(here::here("data", "for_latex"), pattern = "*.txt")

for(i in 1:length(file_names)){
  list_of_tables[[i]] <- readr::read_delim(here::here("data","for_latex", file_names[[i]]), delim = "\t", escape_double = FALSE, trim_ws = TRUE, skip = 1,na = "empty" )
}


names(list_of_tables) <- str_replace(file_names, ".txt", "")


change_names <- function(df){
  names(df) <- str_replace(names(df), "_", "-")
  return(df)
}

list_of_tables <- purrr::map(list_of_tables, change_names)

clean_space <- function(df) {
  df %>%
    mutate_all(~ (str_replace_all(., "%", "\\\\%")))
}

list_of_tables <- purrr::map(list_of_tables, clean_space)


color_significance <- function(df){
  df[-1] <- lapply(
  df[-1], function(x){
    cell_spec(x, background = ifelse(str_count(x, "\\*")==1, "#8C298133", ifelse(str_count(x, "\\*")==2, "#641A8033", ifelse(str_count(x, "\\*")==3, "#3C0F7033", "white"))),color = ifelse(str_count(x, "\\*")>=1, "White", "black" ),bold = ifelse(str_count(x, "\\*")>=1,T, F ))
  }
)
  
  return(df)
}

Groundnut_new <- read_dta("data/for_plot/data_for_descriptive.dta")%>%
  sjlabelled::var_labels(
    year = "Waves of the study",
    country = "Country",
    sales_value = "Sales value",
    prod_value = "Production value",
    gprod = "Total quantity of groundnut harvested",
    formarrach = "Training on groundnut farming",
    cooperative = "Farmers group membership"
  )%>%
  mutate(
    formarrach = haven::as_factor(formarrach),
    cooperative = haven::as_factor(cooperative)
    
  )
my_vars <- c(
  "country",
  "year",
  "adopt",
  "improvsup",
  "sellers",
  "qsale",
  "sales_value",
  "gprod",
  "prod_value",
  "gyield",
  "age",
  "sexe",
  "nbschool",
  "hhsize",
  "cooperative",
  "formagri",
  "formarrach",
  "visitpublic",
  "extension",
  "credite",
  "creditn",
  "dmurbain",
  "dmvillage",
  "crotation",
  "cmixt",
  "nbrhoejour",
  "uprice",
  "cseed_ha",
  "cfert_ha",
  "cpest_ha",
  "clabor_ha",
  "gsize",
  "off_farm",
  "dratio",
  "typsoil1",
  "typsoil2",
  "typsoil3",
  "adopt2y",
  "adopt3y"
)

my_vars_2 <- c(
  "country",
  "year",
  "adopt",
  "age",
  "sexe",
  "nbschool",
  "hhsize",
  "dratio",
  "cooperative_2",
  "formagri",
  "formarrach_2",
  "visitpublic",
  "extension",
  "credite",
  "creditn",
  "dmurbain",
  "dmvillage",
  "crotation",
  "cmixt",
  "nbrhoejour",
  "uprice",
  "cseed_ha",
  "cfert_ha",
  "cpest_ha",
  "clabor_ha",
  "gsize",
  "off_farm",
  "typsoil1",
  "typsoil2",
  "typsoil3"
)

```
\newpage 
# Supplementary Note
We present the results of the estimation using the pooled FE-OLS model. Figure S1 presents the results of the relationship between the adoption of climate-resilient groundnut varieties and commercialization where we employ the linear probability model for binary outcomes. We present results when we consider adoption as a dummy and the extent of adoption of climate-resilient groundnut varieties. Considering adoption as a dummy, we establish a positive association with the commercialization outcomes; market participation, quantity of groundnut sold, and sales. Considering the area under adoption, we obtain negative estimates that are not statistically significant. However, this result could mean that increasing the area of cultivation of improved climate-resilient groundnut varieties is negatively correlated with market participation, quantity sold and the associated sales value. This negative relationship although not statistically significant could be due to diminishing returns when we consider the area under adoption. Otherwise, these negative results could be due to endogeneity issues which could lead to biased estimates. Given that we control for these endogeneity issues using the 2SLS and both household fixed effects and the correlated random effects model, we only use these results for comparison with the main estimation results.


\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{plots/old/plt2.png}
\caption{OLS estimates of the relationship between adoption and commercialization}
\end{figure}
Note: Full models are reported in SM2. Robust standard errors in parentheses. Additional controls include age and educational level of the household head, dependency ratio, whether the household head is male, household size, cooperative membership, training, access to public and private extension, access to credits both in 
\newpage
Estimating the relationship between adoption of improved groundnuts, production, production value and land productivity using the FE-OLS model (Figure S2), we obtain positive coefficients for all outcomes. When we consider adoption as a dummy, we observe production and productivity increases of about 540Kg and 285Kg/ha respectively. Considering the scale of adoption, we observe that adoption of improved climate-smart groundnut varieties increases groundnut production by 240Kg and land productivity by approximately 60Kg/ha. The magnitudes here are positive indicating that adoption both when considered as a dummy as well as extent increases yield, production, and production value. The smaller magnitudes here might be indicative of diminishing returns as early highlighted. The positive and significant estimates of the area under adoption variable aligns with the tenets of the non-separable agricultural household model where the production, consumption and ultimately commercialization decisions of households are non-separable. This suggests that households would only participate in markets to the extent that the household food production and consumption needs are met. 

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{plots/old/plt3.png}
\caption{OLS estimates of the relationship between adoption and commercialization}
\end{figure}
Note: Full models are reported in SM4. Robust standard errors in parentheses). Additional controls include age and educational level of the household head, dependency ratio, whether the household head is male, household size, cooperative membership, training, access to public and private extension, access to credits both in cash and kind, distance to nearest urban and village market, crop rotation, mixed cropping, labour, market price, input costs, area of cultivation, off-farm income and soil type (*** p<0.01, ** p<0.05, * p<0.1)


\newpage
# Descriptive statistics

```{r}
Groundnut_new_2 <- Groundnut_new%>%
  mutate(cooperative_2 = case_when(
    str_detect(cooperative, "Yes") ~ 1,
    TRUE ~ 0
  ),
  formarrach_2 = case_when(
    formarrach=="No" ~ 0,
    TRUE ~ 1
  ))%>%
  sjlabelled::var_labels(
    cooperative_2= "Farmers group membership (dummy)",
    formarrach_2 = "Training on groundnut farming(dummy)"
  )

tbl_strata_ex1 <-
  Groundnut_new_2 %>%
  select(my_vars_2, -c(cooperative,formarrach))%>%
  mutate(adopt = factor(adopt, labels=c("Non-adopter", "Adopter")))%>%
  tbl_strata(
    strata = year,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(
    by=adopt,
    type = list(c(sexe,credite,creditn,formagri) ~ "dichotomous", c(extension)~"continuous"),
    missing = "no",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  )%>% add_p(),
    .header = "**{strata}**, N = {n}"
  )

disc_tbl <- tbl_strata_ex1%>%
  # convert to kableExtra
  as_kable_extra(booktabs = TRUE, longtable = F,caption="Descriptive statistics by year and adoption status") %>%
  # reduce font size to make table fit. 
  # you may also use the `latex_options =  c( c("scale_down", "hold_position"), "hold_position")` argument here.
  kableExtra::kable_styling(font_size = 6, latex_options =  c("scale_down", "hold_position", "repeat_header"))%>%
  kableExtra::landscape()%>%
  row_spec(33, hline_after  = T)
disc_tbl

```
\newpage

# Pooled OLS Regressions

```{r}

df <- list_of_tables$SM1_Table3%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)




kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full OLS estimates of the relationship between adoption and commercialization(Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  kableExtra::kable_paper()
```
\newpage

```{r}

df <- list_of_tables$SM1_Table3_Area%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)



kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full OLS estimates of the relationship between adoption and commercialization (Area under Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

\newpage

```{r}

df <- list_of_tables$SM2_Table4%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = " Full OLS estimates of the relationship between adoption, production and yields(Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

\newpage

```{r}

df <- list_of_tables$SM2_Table4_Area%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr",  caption = "OLS estimates of the relationship between adoption, production and yields(Area under Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
kable_classic("striped", full_width = F)
```
\newpage
# Panel Regression

```{r}

df <- list_of_tables$SM3_Table5%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)%>%
  filter(!stringr::str_detect(variables, 'district') )



kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between adoption and commercialization(Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```
\newpage

```{r}

df <- list_of_tables$SM4_Table6%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between adoption and commercialization (Area under Adoption)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

\newpage

```{r}

df <- list_of_tables$SM5_Table7%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)



kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between adoption, production and yields")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
landscape()
```
\newpage

```{r}

df <- list_of_tables$SM6_adopt_3y%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)%>%
  mutate(
   variables = gsub("\\(.*", "", variables)
  )



kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full 2SLS estimates of the relationship between continous adoption, production and yields")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
landscape()
```


\newpage
# Correlated random effects

```{r}
df <- list_of_tables$cre_tbl_adopt%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full Correlated random effects estimations of the relationship between adoption , commercialization and market orientation")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()
```

```{r}
df <- list_of_tables$cre_tbl_area%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full Correlated random effects estimations of the relationship between adoption (area), commercialization and market orientation")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()
```
\newpage

# Causal mediation analysis

```{r}
df <- list_of_tables$mediation_prod%>%
  rename(variables = VARIABLES)%>%
  mutate(variables = case_when(
    variables == "total" ~ "Total effect (TE)",
    variables == "effect" ~ "Direct effect",
    variables == "direct" ~ "Indirect effect",
    TRUE ~ variables
  ))

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Linear IV mediation analysis of adoption and commercialization (production)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```

```{r}
df <- list_of_tables$mediation_yield%>%
  rename(variables = VARIABLES)%>%
  mutate(variables = case_when(
    variables == "total" ~ "Total effect (TE)",
    variables == "effect" ~ "Direct effect",
    variables == "direct" ~ "Indirect effect",
    TRUE ~ variables
  ))

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Linear IV mediation analysis of adoption and commercialization (Yield)")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```
\newpage

# Cross country analysis

```{r}
df <- list_of_tables$cross_country_t%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F,col.names = c("variables", "Yield", "Commercialization", "Yield", "Commercialization", "Yield", "Commercialization"), align="lrrr", caption = "2SLS estimates of the relationship between  adoption and commercialization and yield across countries")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()%>%
add_header_above(c(" ", "Ghana" = 2, "Mali" = 2, "Nigeria" = 2)) 
```


\newpage

# Robustness checks
\newpage


## Control function approach

```{r}

df <- list_of_tables$SM7_CF_Ro%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full Control function estimations of the relationship between adoption and market participation")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  landscape()
```
\newpage

## Hausman Taylor IV

```{r}

df <- list_of_tables$SM9_HTIV_Ro%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full HAUSMAN TAYLOR IV estimations")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```
\newpage
## Lewbels Test

```{r}

df <- list_of_tables$SM10_LT%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(variables = LABELS)%>%
  mutate(
    #variables = str_remove_all(variables, "(centered)"),
    #variables = str_remove_all(variables, "()"),
    #variables = str_remove_all(variables, "cen"),
    variables = gsub("\\(.*", "", variables)
  )%>%
  filter(MP != "-")

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, align="lrrr", caption = "Full Lewbel instrumental variable estimations of the relationship between adoption and commercialization")%>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))
```


